---
title: "My_Quadratic_Formula"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{My_Quadratic_Formula}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

## Loading the package

```{r setup}
library(WillQuadratic)
```

This package contains a function, `quadratic_formula()`, that can be used to find roots of a quadratic for given coefficients.  It also contains a dataset, 'Pokemon'.  This dataset containts summary statistics for Pokemon, generations 1-6.  This dataset was found on Kaggle.  More information can be found on this dataset [here](https://www.kaggle.com/abcsds/pokemon). 


## Using the `quadratic_formula()` function

The `quadratic_formula()` function finds the roots of a quadratic in the form

$$
ax^2 + bx + c = 0
$$
by taking the coefficients \(a,b,c\) as inputs and applying the quadratic formula

$$
x = \frac{-b \pm \sqrt{b^2-4ac}}{2a}
$$

If the quadratic has one repeated root, the function returns a numeric with that value.  If the quadratic has distint, real roots, the function returns a vector of numerics containing the solutions.  If the quadratic has non-real roots, the vector of solutions contains objects of class complex.

\vspace{1cm}

## Example 1 - Repeated root

Consider the quadratic

$$
x^2 - 10x + 25 = 0
$$
That is, \(a=1,b=-10,c=25\), we would expect

$$
\begin{aligned}
x = \frac{10 \pm \sqrt{(-10)^2 - 4(25)}}{2} \\[1em]
= \frac{10 \pm \sqrt{100 - 100}}{2} \\[1em]
= 5
\end{aligned}
$$
Hence, using `quadratic_formula()` we have

```{r}
quadratic_formula(1, -10, 25)
```

\vspace{1cm}

## Example 2 - Distinct, real roots

Consider the quadratic 

$$
2x^2 - 10x + 12 = 0 
$$
That is, \(a=2, b=-10, c=12\), we would expect

$$
\begin{aligned}
x = \frac{10 \pm \sqrt{(-10)^2 - 4(2)(12)}}{2(2)} \\[1em]
= \frac{10 \pm \sqrt{100 - 96}}{4} \\[1em]
= \frac{10 \pm 2}{4} \\[1em]
= 2,3
\end{aligned}
$$
Hence, using `quadratic_formula()` we have

```{r}
quadratic_formula(2, -10, 12)
```


## Example 3 - Non-real roots

Consider the quadratic

$$
x^2 - 2x + 2 = 0
$$
That is, \(a=1, b=-2, c=2\), we would expect

$$
\begin{aligned}
x = \frac{2 \pm \sqrt{(-2)^2 - 4(2)}}{2} \\[1em]
= \frac{2 \pm \sqrt{4 - 8}}{2} \\[1em]
= \frac{2 \pm \sqrt{-4}}{2} \\[1em]
= 1 \pm \sqrt{-1} \\[1em]
= 1 + i, 1-i
\end{aligned}
$$
Hence, using `quadratic_formula()` we have

```{r}
x <- quadratic_formula(1, -2, 2)
x
class(x)
```
